\tool: Revisiting BadUSB with Type-C

### 2021-03-06 WOOT/Files/related_work.tex
related work

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decides whether to authorize. When a device
is plugged in, GoodUSB loads its driver but limits its functionality until a
series of authorizations are completed. These authorizations are designed to be
performed manually. As BadUSB is normally unable to obtain the video stream of
the host, an attacker cannot complete this authorization with
an automatic script. Thus this defense is sufficient for a normal BadUSB attack. But
if the attacker has the access to victim's screen, GoodUSB would be bypassed
easily as the attacker can complete this authorization manually and
perform subsequent attacks.

@@

Therefore, there exists a clear trade-off between the effectiveness and the
plug-and-play property. Though hardware disabling solutions like USB Condom
archives almost absolute security, the functionality of USB is sacrificed.
Other solutions like GoodUSB or whitelist are either bypassable or insufficient
under certain scenarios. Vendors may sacrifice complete security to
improve usability, which allows attackers to take advantage of.

@@

		\hline
		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty\\
		\hline

>>>>

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decides whether to authorize. When a device
is plugged in, GoodUSB limits its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected for making a different claim 
that does not match the authorization results. USBeSafe\cite{usbesafe} analyses the 
feature vector constructed from with data collected from USB Request Block(URBs), 
it would detect the novel USB packets based on the machine learning algorithm and send 
a alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.

@@

Therefore, there exists a clear trade-off between the effectiveness and the
plug-and-play property. Though hardware disabling solutions like USB Condom
archives almost absolute security, the functionality of USB is sacrificed.
Other solutions like whitelist are either bypassable or insufficient
under certain scenarios. Vendors may sacrifice complete security to
improve usability, which allows attackers to take advantage of.

@@

		\hline
		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circlefull\\
		\hline
